On the Synchronization of Computational RFIDs

### 2018-05-13 TMC-2017-11-0695-main.tex
Section 2.2 of the paper revised

The focus of this article is to answer the question of \emph{how to design a building block that synchronizes intermittently-powered CRFID systems?} To this end, we investigate the WISP platform and provide initial observations and limitations pertaining to the synchronization of these devices. In particular, the main contributions and findings of 
this article are:
%
\begin{itemize}
	\item To the best of our knowledge, this is the first study that focuses on the synchronization of tags in CRFID systems. Even though there are studies on the synchronization of multiple RFID readers, e.g.~\cite{reader_sync}, we are unaware of any study that provides synchronization of individual tags in the communication range of an RFID reader. 
	\item By addressing the aforementioned challenges, we design and implement \emph{the first synchronization primitive} for the tags, namely \emph{WISP-Sync}, inspired by the Proportional-Integral (PI) controllers~\cite{pi2015,yildirim2017adaptive}. WISP-Sync (i) 
	requires only a few computation steps to run efficiently under limited harvested energy and keeps a few variables to hold the synchronization state to recover from power interruptions with minimum overhead---\emph{addressing Challenge I}; (ii) is adaptive to react to clock instabilities in a fast manner---\emph{addressing Challenge II}.
	\item \add{Our time synchronization algorithms compensate for the clock drift and provide access to an \emph{explicit clock} for CRFID applications. Moreover, our implementations are independent of how EPC Gen2 is implemented ---providing a level of portability across different platforms.}
	%
	\item We provide theoretical analysis to prove that this primitive establishes synchronization and to reveal the factors affecting its synchronization performance.
	%
	\item Evaluations in our testbed show that an average synchronization error of approximately 1\,ms can be ensured among tags with an energy overhead of 1.85\,$\mu$J per synchronization round using this  primitive.
\end{itemize}
%
We note that WISP-side implementations throughout the article are done using C and assembly language. All source codes and scripts used to generate the results in the article (including parsing, post-processing and measurement results) are available via~\href{https://goo.gl/RuWIZ2}{https://goo.gl/RuWIZ2}.

@@

\add{\subsubsection{Slot and Bit-level Synchronization}
EPC Gen2 requires slot-level synchronization to implement slotted Aloha protocol. This is achieved by adjusting clock offsets upon reception from the reader and introducing guard times to ensure that tags communicate at the
allocated frame boundaries. It is also possible to exploit modulation
properties of signals from the reader to the tags (such as bit timing in FM0 modulation) in order to get the timing measurements of the regular patterns in the signal, i.e. bit-level synchronization~\cite{liu_tcomp_2015,liu_ton_2017,liu2_ton_2017}. However, neither slot nor bit level synchronization compensate for clock drifts and output a synchronized clock value that can be accessed by the tags. 
}

>>>>

The focus of this article is to answer the question of \emph{how to design a building block that synchronizes intermittently-powered CRFID systems?} To this end, we investigate the WISP platform and provide initial observations and limitations pertaining to the synchronization of these devices. In particular, the main contributions and findings of 
this article are:
%
\begin{itemize}
	\item To the best of our knowledge, this is the first study that focuses on the synchronization of tags in CRFID systems. Even though there are studies on the synchronization of multiple RFID readers, e.g.~\cite{reader_sync}, we are unaware of any study that provides synchronization of individual tags in the communication range of an RFID reader. 
	\item By addressing the aforementioned challenges, we design and implement \emph{the first synchronization primitive} for the tags, namely \emph{WISP-Sync}, inspired by the Proportional-Integral (PI) controllers~\cite{pi2015,yildirim2017adaptive}. WISP-Sync (i) 
	requires only a few computation steps to run efficiently under limited harvested energy and keeps a few variables to hold the synchronization state to recover from power interruptions with minimum overhead---\emph{addressing Challenge I}; (ii) is adaptive to react to clock instabilities in a fast manner---\emph{addressing Challenge II}.
	\item \add{Our time synchronization algorithms compensate for the clock drift and provide access to an \emph{explicit clock} for CRFID applications. Moreover, our implementations are independent of how EPC Gen2 is implemented---providing a level of portability across different platforms.}
	%
	\item We provide theoretical analysis to prove that this primitive establishes synchronization and to reveal the factors affecting its synchronization performance.
	%
	\item Evaluations in our testbed show that an average synchronization error of approximately 1\,ms can be ensured among tags with an energy overhead of 1.85\,$\mu$J per synchronization round using this  primitive.
\end{itemize}
%
We note that WISP-side implementations throughout the article are done using C and assembly language. All source codes and scripts used to generate the results in the article (including parsing, post-processing and measurement results) are available via~\href{https://goo.gl/RuWIZ2}{https://goo.gl/RuWIZ2}.

@@

\add{\subsubsection{Slot and bit-level synchronization} EPC Gen2 requires a slot-level synchronization to implement slotted Aloha protocol. This is achieved by adjusting clock offsets upon reception from the reader and introducing guard times to ensure that tags communicate at the
allocated frame boundaries. It is also possible to exploit modulation properties of signals from the reader to the tags (such as bit timing in FM0 modulation) in order to get the timing measurements of the regular patterns in the signal, i.e. bit-level synchronization~\cite{liu_tcomp_2015,liu_ton_2017,liu2_ton_2017}. However, neither slot nor bit level synchronization compensate for clock drifts and output a synchronized clock value that can be accessed by the tags.}
